|

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.Rmd
captions on Effect size

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_point(data = ~.x %>% 
             group_by(log_effect_size, reject) %>% 
             summarise(num_response = n()),
           aes(log_effect_size, reject, size = factor(num_response)), alpha = 0.3)  +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(log_effect_size, reject, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  theme_light(base_size = 5) +
  theme(panel.grid.major.x =  element_line(colour = "grey70", linewidth = 0.5)) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "# lineups")
```

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject, size = factor(num_response)), alpha = 0.3) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(log_effect_size, reject, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  theme_light(base_size = 5) +
  theme(panel.grid.major.x =  element_line(colour = "grey70", linewidth = 0.5)) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "# lineups")
```

@@

Figure \ref{fig:poly-example} shows one of the ten lineups where the visual test rejected the residual plot. The data plot, in position three is very obvious, and different from the nulls. The visual test was correct to reject. To understand why this is, one needs to return to the way the RESET test is applied. It requires a parameter indicating degree of polynomial to test for, and the recommendation is to generically use 4 (XXX REF). However, the "M" and the "Triple-U" shapes constructed from the Hermite polynomials use power up to 6 and 18 respectively. All 10 lineups rejected by the visual test but not the RESET were of types "M" or "Triple-U". If the RESET test had been applied using the power up to 6, all the decisions for these lineups would have been to reject. The recommendation of the polynomial power for the RESET should be revised, perhaps. This illustrates the sensitivity of conventional testing to the parameters, and it also points to a limitation that one needs to know the data structure in order to set the parameters for the test.

@@

```{r}
poly_conv_sim %>%
  filter(x_dist == "uniform", shape %in% c(3, 4)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(shape, log_effect_size, (RESET3_p_value:RESET9_p_value)) %>%
  pivot_longer(RESET3_p_value:RESET9_p_value) %>%
  mutate(name = gsub("_p_value", " ", name)) %>%
  mutate(name = gsub("RESET", "", name)) %>%
  mutate(name = gsub("test", "", name)) %>%
  mutate(reject = as.numeric(value < 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = name), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  scale_color_manual(values = rev(rcartocolor::carto_pal(7, "RedOr"))) +
  theme_light() +
  labs(col = "RESET test order") +
  facet_wrap(~shape)
```

```{r}
heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Conventional test")
```

```{r}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Visual test")
```

@@

dat_different_dist %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(1,3,2,4)]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "Distribution of regressor", linetype = "Test") +
  facet_wrap(~conv_or_not)
```

>>>>

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_point(data = ~.x %>% 
             group_by(log_effect_size, reject) %>% 
             summarise(num_response = n()),
           aes(log_effect_size, reject, size = factor(num_response)), alpha = 0.3)  +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(log_effect_size, reject, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  theme_light(base_size = 5) +
  theme(panel.grid.major.x =  element_line(colour = "grey70", linewidth = 0.5)) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", size = "# lineups")
```

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject, size = factor(num_response)), alpha = 0.3) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject, times = 500), 
              aes(log_effect_size, reject, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  theme_light(base_size = 5) +
  theme(panel.grid.major.x =  element_line(colour = "grey70", linewidth = 0.5)) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", size = "# lineups")
```

@@

Figure \ref{fig:poly-example} shows one of the ten lineups where the visual test rejected the residual plot. The data plot, in position three, is very obvious, and different from the nulls. The visual test was correct to reject. To understand why this is, one needs to return to the way the RESET test is applied. It requires a parameter indicating degree of polynomial to test for, and the recommendation is to generically use 4 (XXX REF). However, the "M" and the "Triple-U" shapes constructed from the Hermite polynomials use power up to 6 and 18 respectively. All 10 lineups rejected by the visual test but not the RESET were of types "M" or "Triple-U". If the RESET test had been applied using the power up to 6, all the decisions for these lineups would have been to reject. The recommendation of the polynomial power for the RESET should be revised, perhaps. This illustrates the sensitivity of conventional testing to the parameters, and it also points to a limitation that one needs to know the data structure in order to set the parameters for the test.

@@

```{r}
poly_conv_sim %>%
  filter(x_dist == "uniform", shape %in% c(3, 4)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(shape, log_effect_size, (RESET3_p_value:RESET9_p_value)) %>%
  pivot_longer(RESET3_p_value:RESET9_p_value) %>%
  mutate(name = gsub("_p_value", " ", name)) %>%
  mutate(name = gsub("RESET", "", name)) %>%
  mutate(name = gsub("test", "", name)) %>%
  mutate(reject = as.numeric(value < 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = name), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rev(rcartocolor::carto_pal(7, "RedOr"))) +
  theme_light() +
  labs(col = "RESET test order") +
  facet_wrap(~shape)
```

```{r}
heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Conventional test")
```

```{r}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Visual test")
```

@@

dat_different_dist %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(1,3,2,4)]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "Distribution of regressor", linetype = "Test") +
  facet_wrap(~conv_or_not)
```
